\textbf{Appendix}\\ Bound within Boundaries: How Well Do Protected Areas Match Movement Corridors of Their Most Mobile Protected Species?

### 2020-09-23 Chapter_0/04_Manuscript/Manuscript.tex
Finalized Revision

\noindent 4. Differences in permeability were mainly related to different
degrees of human activities across regions, and to the presence or absence of
rivers, swamps or open water. The relation between permeability and other
landscape features was less evident.

@@

\subsection{Least-Cost Paths and Corridors}
To identify movement corridors of dispersing wild dogs, we specified source
points and calculated factorial least-cost paths (LCPs) as well as factorial
least-cost corridors (LCCs) among them \citep{Elliot.2014}. We generated source
points by overlaying the study area with a regular grid of points spaced at 100
km. We only considered those points that fell within protected areas \(>\) 700
km\textsuperscript{2}, which conforms with home-range requirements of African
wild dogs \citep{Pomilia.2015}. Finally, we defined centroids as source points
for those protected areas \(>\) 700 km\textsuperscript{2} that were not assigned
any source points from the regular grid. Because wild dogs residing outside of
protected areas are rare and unviable \citep{VanDerMeer.2014}, we consider our
selection of source points within protected areas to be appropriate. In total,
we generated 68 source points, which resulted in 2'278 unique pairwise
combinations and therefore 2'278 unique LCPs and LCCs. We computed factorial
LCPs and LCCs between source points using the R-package \textit{gdistance}
(further details in Appendix A.7). After computation, we tallied overlapping
LCPs and LCCs, respectively, into single connectivity maps. Because LCPs return
discrete paths, whereas LCCs return continuous corridors, we present both
methods.

@@

Although dispersers avoided moving through water, they selected locations in its
vicinity. This behavior may be caused by the occurence of prey close to water
\citep{Bonyongo.2005}. For the same reason, however, competitors such as lions,
spotted hyenas, and resident wild dogs may also use areas close to water
\citep{Valeix.2010}, thereby occasionally forcing dispersing wild dogs to switch
behavior and move into prey-poorer areas away from water \citep{Creel.2002,
Mills.1997}. This reasoning may also explain the large confidence intervals
surrounding the corresponding \(\beta\)-estimate. Given the influence that
resident conspecifics, competitors, and prey can have on dispersers
\citep{Cozzi.2018, Armansin.2019} future studies should strive to collect and
incorporate intra- and interspecific relationships into analyses of landscape
connectivity.

Overall, our findings on habitat selection during dispersal coincide with
findings from dipsersing wild dogs in Kenya \citep{Oneill.2020}, suggesting that
there are strong commonalities between dispersers from these very different
ecosystems. Thus, despite wild dogs' ability to cope with diverse habitats and
adapt to changing conditions \citep{Woodroffe.2011}, the fundamental factors
included in our study appear to influence wild dogs from other ecosystems alike.
Nevertheless, expanding our analysis to dispersers emigrating from other source
populations would invaluably contribute to our understanding of dispersal.

@@

Besides estimating corridors, individual based simulations may be used to
generate permeability surfaces \citep{Avgar.2016, Signer.2017}. Such surfaces
have been shown to reduce the risk of overestimating \(w(x)\) and conesquently
connectivity, particularly in areas that lie far from suitable habitats
\citep{Signer.2017}. While a simulation-based approach is conceptually
straightforward, computational requirements are high, especially for such a
large extent as constituted by the KAZA-TFCA.

@@

\section{Data Availability}
GPS movement data of dispersing coalitions will be made available on dryad at
the time of publication. We will also provide example R-code on Github to
demonstrate our least-cost modelling approach
(\url{https://github.com/DavidDHofmann}).

>>>>

\noindent 4. Differences in permeability were mainly related to different
degrees of human activities across regions, and to the presence or absence of
rivers, swamps or open water. The relationship between permeability and other
landscape features was less pronounced.

@@

\subsection{Least-Cost Paths and Corridors}
To identify movement corridors of dispersing wild dogs, we specified source
points and calculated factorial least-cost paths (LCPs) as well as factorial
least-cost corridors (LCCs) among them \citep{Elliot.2014}. We generated source
points by overlaying the study area with a regular grid of points spaced at 100
km. We only considered those points that fell within protected areas \(>\) 700
km\textsuperscript{2}, which conforms with home-range requirements of African
wild dogs \citep{Pomilia.2015}. Finally, we defined centroids as source points
for those protected areas \(>\) 700 km\textsuperscript{2} that were not assigned
any source points from the regular grid. Because wild dogs residing outside of
protected areas are rare and unviable \citep{VanDerMeer.2014}, we consider our
selection of source points within protected areas to be appropriate. In total,
we generated 68 source points, which resulted in 2'278 unique pairwise
combinations and therefore 2'278 unique LCPs and LCCs. We computed factorial
LCPs and LCCs between source points using the R-package \textit{gdistance}
(further details in Appendix A.7). After computation, we tallied overlapping
LCPs and LCCs, respectively, into single connectivity maps. Because LCPs return
discrete paths, whereas LCCs return continuous corridors, we present both
methods. R-codes showcasing the main steps for sections 2.5 to 2.6 can be
downloaded from GitHub
(\url{https://github.com/DavidDHofmann/LeastCostAnalysis}).

@@

Although dispersers avoided moving through water, they selected locations in its
vicinity. This behavior may be caused by the occurence of prey close to water
\citep{Bonyongo.2005}. For the same reason, however, competitors such as lions,
spotted hyenas, and resident wild dogs may also use areas close to water
\citep{Valeix.2010}, thereby occasionally forcing dispersing wild dogs to switch
behavior and move into prey-poorer areas away from water \citep{Creel.2002,
Mills.1997}. This may explain the large confidence intervals for the
corresponding \(\beta\)-estimate of \textit{distance to water}. Given the
influence that resident conspecifics, competitors, and prey can have on
dispersers \citep{Cozzi.2018, Armansin.2019} future studies should strive to
collect and incorporate intra- and interspecific relationships into analyses of
landscape connectivity.

Overall, our findings on habitat selection during dispersal coincide with
findings from dipsersing wild dogs in Kenya \citep{Oneill.2020} and Tanzania
\citep{Masenga.2016}, suggesting that there are strong commonalities between
dispersers from these very different ecosystems. Thus, despite wild dogs'
ability to cope with diverse habitats and adapt to changing conditions
\citep{Woodroffe.2011}, the fundamental factors included in our study appear to
influence wild dogs from other ecosystems alike. Nevertheless, expanding our
analysis to dispersers emigrating from other source populations would invaluably
contribute to our understanding of dispersal.

@@

Besides estimating corridors, individual based simulations may be used to
generate permeability surfaces \citep{Avgar.2016, Signer.2017}. Such surfaces
have been shown to reduce the risk of overestimating \(w(x)\) and conesquently
connectivity, particularly in areas that lie far from suitable habitats
\citep{Signer.2017}. While a simulation-based approach is conceptually
straightforward, computational requirements for such a large spatial extent as
the KAZA-TFCA are very high, making the use of this approach challenging. We
urge future studies to optimize the simulation of corridors from iSSFs that
capture a more mechanistic model of dispersal.

@@

\section{Data Availability}
GPS movement data of dispersing coalitions will be made available on dryad at
the time of publication. R-code showcasing the main steps for sections 2.5 to
2.6 can be downloaded from GitHub
(\url{https://github.com/DavidDHofmann/LeastCostAnalysis}).

### 2020-09-23 Chapter_0/04_Manuscript/Manuscript_Support.tex
Finalized Revision

%------------------------------------------------------------------------------
%	Appendix S2: GPS Data
%------------------------------------------------------------------------------
\newpage
\section{GPS Data}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.86\textwidth]{99_Trajectories.pdf}
    \caption{Illustration of all trajectories that we recorded. Each color
    represents a different dispersing coalition. All coalitions departed from
    the area which is indicated by the white dashed rectangle. The coalition
    dispersing towards the far east of the map covered over 360 km in under 10
    days. Satellite background imagery was provided by Microsoft Bing.}
    \label{Trajectories}
  \end{center}
\end{figure}

\begin{table}[hbtp]
  \caption{Summary statistics of all GPS relocations that have been recorded on
  dispersing coalitions.}
  \label{GPSData}
  \begin{center}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{lccccccc}
      \toprule
      \parbox[]{2cm}{\centering Coalition ID} &
        \parbox[]{1cm}{\centering Sex} &
          \parbox[]{2cm}{\centering \ Pack \\ Affiliation} &
            \parbox[]{1.5cm}{\centering \# Fixes \\ Total} &
              \parbox[]{1.5cm}{\centering \# Fixes \\ During \\ Dispersal} &
                \parbox[]{1.5cm}{\centering \# Days \\ Dispersing} &
                  \parbox[]{2cm}{\centering Euclidean \\ Dispersal\\ Distance \\ (in km)} &
                    \parbox[]{2cm}{\centering Cumulative \\ Dispersal \\ Distance \\ (in km)} \\
      \midrule
      Abel & M & MU & 894 & 45 & 9 & 131 & 205 \\
      Amacuro & F & MB & 954 & 583 & 137 & 23 & 1'090 \\
      Belgium & M & ZU & 1'097 & 158 & 28 & 18 & 319 \\
      Dalwhinnie & F & PA & 545 & 62 & 22 & 50 & 243 \\
      Denali & F & MN & 1'096 & 173 & 33 & 11 & 528 \\
      Everest & M & MN & 389 & 123 & 38 & 67 & 572 \\
      Kalahari & F & HT & 1'753 & 467 & 130 & 20 & 1'963 \\
      Karisimbi & M & MN & 438 & 141 & 34 & 45 & 251 \\
      Liuwa & F & AP & 946 & 92 & 19 & 144 & 451 \\
      Lupe & M & KW & 2'209 & 396 & 34 & 8 & 436 \\
      MadameChing & F & AP & 776 & 729 & 136 & 263 & 1'560 \\
      Mirage & M & HT & 814 & 182 & 36 & 7 & 435 \\
      Odzala & M & AP & 1'410 & 205 & 42 & 53 & 412 \\
      Scorpion & M & KB & 2'676 & 393 & 34 & 4 & 471 \\
      Stetson & M & MT & 384 & 383 & 33 & 3 & 481 \\
      Taryn & F & AP & 896 & 37 & 9 & 10 & 130 \\
      \toprule
      \toprule
      \textit{Mean} & - & - & 1'080 & 261 & 48 & 54 & 597 \\
      \textit{(SD)} & - & - & (649) & (207) & (44) & (71) & (508) \\
      \bottomrule
      \end{tabular}
    }
  \end{center}
\end{table}

@@

%------------------------------------------------------------------------------
%  Appendix S6: Random Effects Variability
%------------------------------------------------------------------------------
\newpage
\section{Habitat Selection Model: Random Effects}
\begin{figure}[hbtp]
  \includegraphics[width = \textwidth]{99_RandomEffects}
  \caption{Plot of random effects showing variability across dispersal
  coalitions.}
  \label{RandomEffects}
\end{figure}

>>>>

%------------------------------------------------------------------------------
%	Appendix S2: GPS Data
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{GPS Data}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.84\textwidth]{99_Trajectories.pdf}
    \caption{Illustration of all trajectories that we recorded. Each color
    represents a different dispersing coalition. All coalitions departed from
    the area which is indicated by the white dashed rectangle. The coalition
    dispersing towards the far east of the map covered over 360 km in under 10
    days. Satellite background imagery was provided by Microsoft Bing.}
    \label{Trajectories}
  \end{center}
\end{figure}

\begin{table}[hbtp]
  \caption{Summary statistics of all GPS relocations that have been recorded on
  dispersing coalitions. The coalition ID refers to the individual in the
  dispersal coalition that was equipped with a GPS collar. All coalitions
  consisted of same-sex individuals.}
  \label{GPSData}
  \begin{center}
    \resizebox{0.95\textwidth}{!}{
      \begin{tabular}{lccccccc}
      \toprule
      \parbox[]{2cm}{\centering Coalition ID} &
        \parbox[]{1cm}{\centering Sex} &
          \parbox[]{2cm}{\centering \ Pack \\ Affiliation} &
            \parbox[]{1.5cm}{\centering \# Fixes \\ Total} &
              \parbox[]{1.5cm}{\centering \# Fixes \\ During \\ Dispersal} &
                \parbox[]{1.5cm}{\centering \# Days \\ Dispersing} &
                  \parbox[]{2cm}{\centering Euclidean \\ Dispersal\\ Distance \\ (in km)} &
                    \parbox[]{2cm}{\centering Cumulative \\ Dispersal \\ Distance \\ (in km)} \\
      \midrule
      Abel & M & MU & 894 & 45 & 9 & 131 & 205 \\
      Amacuro & F & MB & 954 & 583 & 137 & 23 & 1'090 \\
      Belgium & M & ZU & 1'097 & 158 & 28 & 18 & 319 \\
      Dalwhinnie & F & PA & 545 & 62 & 22 & 50 & 243 \\
      Denali & F & MN & 1'096 & 173 & 33 & 11 & 528 \\
      Everest & M & MN & 389 & 123 & 38 & 67 & 572 \\
      Kalahari & F & HT & 1'753 & 467 & 130 & 20 & 1'963 \\
      Karisimbi & M & MN & 438 & 141 & 34 & 45 & 251 \\
      Liuwa & F & AP & 946 & 92 & 19 & 144 & 451 \\
      Lupe & M & KW & 2'209 & 396 & 34 & 8 & 436 \\
      MadameChing & F & AP & 776 & 729 & 136 & 263 & 1'560 \\
      Mirage & M & HT & 814 & 182 & 36 & 7 & 435 \\
      Odzala & M & AP & 1'410 & 205 & 42 & 53 & 412 \\
      Scorpion & M & KB & 2'676 & 393 & 34 & 4 & 471 \\
      Stetson & M & MT & 384 & 383 & 33 & 3 & 481 \\
      Taryn & F & AP & 896 & 37 & 9 & 10 & 130 \\
      \toprule
      \toprule
      \textit{Mean} & - & - & 1'080 & 261 & 48 & 54 & 597 \\
      \textit{(SD)} & - & - & (649) & (207) & (44) & (71) & (508) \\
      \bottomrule
      \end{tabular}
    }
  \end{center}
\end{table}
\restoregeometry

@@

%------------------------------------------------------------------------------
%  Appendix S6: Random Effects Variability
%------------------------------------------------------------------------------
\newpage
\section{Habitat Selection Model: Random Effects}
\begin{figure}[hbtp]
  \includegraphics[width = \textwidth]{99_RandomEffects}
  \caption{Plot of random effects showing variability across dispersal
  coalitions. The coalition ID refers to the individual in the dispersal
  coalition that was equipped with a GPS collar.}
  \label{RandomEffects}
\end{figure}
